Races with hyper3 objects

### 2022-04-17 inst/race3.Rmd
pnames<-.hyper3()

@@

```{r,dotheconst}
jj <- read.table("constructor_2021.txt",header=TRUE)
constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:10]
```

@@

```{r,maketheconst,cache=TRUE}
constructor_2021 <- ordertable2supp3(constructor_table_2021)
```

@@

```{r,label=maxconstr,cache=TRUE}
mc <- maxp(constructor_2021)
mc
```

```{r,label=drawaconstructorpie}
pie(mc)
```

@@

and fail to reject that null.

>>>>

Now consider

$$a\succ b\succ c\succ a$$

with likelihood function

$$
\mathcal{L} =
\frac{a}{2a+b+c}\cdot
\frac{b}{ a+b+c}\cdot
\frac{c}{ a  +c},\qquad a+b+c=1$$

It can be shown that this has a maximum if $a^3+4a^2+4a-1=0$.
Although cubic equations have analytical roots, the expression is
complicated, and equal to about `c(a=0.2056,b=0.5466,c=0.2478)`:

```{r,label=abca,cache=TRUE}
maxp(ordervec2supp3(c("a","b","c","a")))
```

@@

```{r,dotheconst}
jj <- read.table("constructor_2021.txt",header=TRUE)
i <- seq(from=1,by=2,to=nrow(jj)) # extract every second entry for points
constructor_points_2021 <- jj[i,ncol(jj)]
names(constructor_points_2021) <- jj[i,1]

constructor_points_2021 <- sort(constructor_points_2021,dec=TRUE)
constructor_points_2021

constructor_table_2021 <- jj[,-ncol(jj)]
constructor_table_2021[,1:10]
```

@@

```{r,maketheconst,cache=TRUE}
constructor_2021 <- ordertable2supp3(constructor_table_2021)
pnames(constructor_2021) <- names(constructor_points_2021)
```

@@

```{r,label=maxconstr,cache=TRUE}
constructor_2021_maxp <-  maxp(constructor_2021)
mc <- constructor_2021_maxp  # saves typing
```

```{r,label=drawaconstructorpie}
pie(mc)
dotchart(mc,pch=16)
ordertransplot(rank(-mc),rank(-constructor_points_2021),xlab="likelihood rank",ylab="points rank")
```

@@

and fail to reject that null.  How about the mid-range constructors:

```{r,label=testsameconstructorlowscores,cache=TRUE}
samep.test(constructor_2021,c("ATH","ARRF","AR","AMM")) # ~ 10 mins
```

### Package dataset {-}

Following lines create `constructor.rda`, residing in the `data/`
directory of the package.

```{r,label=saveconstructordataset}
save(constructor_2021_maxp,constructor_2021,constructor_table_2021,file="constructor.rda")
```
